---
title: "contour()"
author: "Kyle Brewster"
output:
  slidy_presentation: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# A Simple Example
<body style="background-color:LightGray;">

```{r}
x <- -10:10
y <- -10:10
z <- sqrt(outer(x ^ 2, y ^ 2, "+"))

contour(x,y,z)
```

# Example with Data 

Using base `volcano` data set containing data on Auckland's (NZ) Maungawhau Volcano (Mt. Eden)
- provides volcano height in 10x10 meter grids

```{r message=FALSE, warning=FALSE}
tibble::as.tibble(volcano)
```

# Using the basic plot

```{r}
contour(volcano)
```

# Adjusting size and style of contour lines

```{r}
contour(volcano,
        lwd = 2,
        lty = 8)
```

# Assign different labels

```{r}
contour(volcano,
        lwd = 2,
        lty = 8,
        labels = c("A","B","C","D"))
```


# Changing contour label text size

```{r}
contour(volcano,
        lwd = 3,
        lty = 5,
        labels = c("A","B","C","D"),
        labcex = 1)
```

# Or removing the labels altogether

```{r}
contour(volcano,
        lwd = 3,
        lty = 5,
        drawlabels = F)
```

# And removing the frame and axes

```{r}
contour(volcano,
        lwd = 3,
        lty = 5,
        drawlabels = F,
        frame.plot = F,
        axes = F)
```

# Can also create a filled contour mapping
```{r}
filled.contour(volcano)
```

# Define the number of levels
```{r}
filled.contour(volcano,
               nlevels = 30)
```

# Modify color schemes
```{r}
filled.contour(volcano,
               nlevels = 30,
               color.palette = terrain.colors)
```

# Adding contour line over the filled contour
```{r}

filled.contour(volcano,
               nlevels = 30,
               color.palette = terrain.colors,
               plot.axes = {
                   axis(1)
                   axis(2)
                   contour(volcano, add = TRUE, lwd = 2)
               })
```



